GMSE: a general tool for management strategy evaluation

### 2017-09-18 notebook/presentation/GMSE_presentation.Rmd
Minor tweaks for shiny

 - **Asymmetric payoffs**: Payoffs of choices may depend instead on stakeholder identity.

@@

 - **Asymmetric payoffs**: Payoffs of choices may depend instead on stakeholder identity.
  - **Multiple choices**: Players might have three or more choices.

@@

 - **Asymmetric payoffs**: Payoffs of choices may depend instead on stakeholder identity.
 - **Multiple choices**: Players might have three or more choices.
 - **Multiple players**: More than two stakeholders might interact at one time.

@@

 - **Asymmetric payoffs**: Payoffs of choices may depend instead on stakeholder identity.
 - **Multiple choices**: Players might have three or more choices.
 - **Multiple players**: More than two stakeholders might interact at one time.
 - **Iterated interactions**: Strategies maybe affected by interaction history.

@@

## Genearlised MSE {.smaller}

@@

- Integrates game theory and ecological theory to construct social-ecological models for adaptive management
- Simulates all aspects of management: population dynamics, manager observation of populations, manager decision making, and stakeholder responses to management decisions
- Mimic the decision-making process of managers and stakeholders under conditions of change, uncertainty, and conflict
- Provide a flexible modelling framework for future development of complex adaptive management models to be applied to conservation theory and specific case studies

@@

## Genearlised MSE ('GMSE' R package)

@@

- One manager analyses observations and compares with a target abundance
- Five possible policy options (scaring, culling, castration, feeding, helping)
- Fixed budget and a costs for setting policy
- Genetic algorithm anticipates policy effects from previous actions to set costs of actions for stakeholders

@@

```{r, echo = TRUE}
sim <- gmse(land_ownership = TRUE, stakeholders = 10, RESOURCE_ini = 1000,
            res_death_K = 2000, manage_target = 1000, res_consume = 1,
            user_budget = 5000, manager_budget = 5000, plotting = FALSE,
            scaring = TRUE, culling = TRUE, observe_type = 1, fixed_mark = 50, 
            fixed_recapt = 300);
```

@@

**Plot of conflict among stakeholders**

>>>>

 - **Asymmetric payoffs**: Payoffs of choices may depend instead on stake-holder identity.

@@

 - **Asymmetric payoffs**: Payoffs of choices may depend instead on stake-holder identity.
  - **Multiple choices**: Players might have three or more choices.

@@

 - **Asymmetric payoffs**: Payoffs of choices may depend instead on stake-holder identity.
 - **Multiple choices**: Players might have three or more choices.
 - **Multiple players**: More than two stake-holders might interact at one time.

@@

 - **Asymmetric payoffs**: Payoffs of choices may depend instead on stake-holder identity.
 - **Multiple choices**: Players might have three or more choices.
 - **Multiple players**: More than two stake-holders might interact at one time.
 - **Iterated interactions**: Strategies maybe affected by interaction history.

@@

## Generalised MSE {.smaller}

@@

- Integrates game theory and ecological theory to construct social-ecological models for adaptive management
- Simulates all aspects of management: population dynamics, manager observation of populations, manager decision making, and stake-holder responses to management decisions
- Mimic the decision-making process of managers and stake-holders under conditions of change, uncertainty, and conflict
- Provide a flexible modelling framework for future development of complex adaptive management models to be applied to conservation theory and specific case studies

@@

## Generalised MSE ('GMSE' R package)

@@

- One manager analyses observations and compares with a target abundance
- Five possible policy options (scaring, culling, castration, feeding, helping)
- Fixed budget and a costs for setting policy
- Genetic algorithm anticipates policy effects from previous actions to set costs of actions for stake-holders

@@

```{r, echo = TRUE}
sim <- gmse(land_ownership = TRUE, stakeholders = 10, RESOURCE_ini = 1000,
            res_death_K = 2000, manage_target = 1000, res_consume = 1,
            manager_budget = 5000, user_budget = 5000, plotting = FALSE,
            scaring = TRUE, culling = TRUE, observe_type = 1, fixed_mark = 50, 
            fixed_recapt = 300);
```

@@

**Plot of conflict among stake-holders**
